Exploring Bounds

### 2015-04-14 draft.tex
almost finished with proof of Plotkin

\begin{comment}

@@

Plotkin
talk about importance
define it
prove it
work out some examples

@@

\end{comment}

>>>>

\section{Upper Bounds}

\subsection{Plotkin Upper Bound}
%Plotkin
%talk about importance
%define it
%prove it
%work out some examples

The Plotkin Bound is an upper bound that often improves upon the Sphere Packing Bound on $A_q(n,d)$.  It is limited, however, in that it is only valid when $d$ is sufficiently
close to $n$.  Consider that for $q=2$ our restriction is $n<2d$,  for $q=3$ our restriction is $n<\frac{3}{2}d$, for $q=4$ our restriction is $n<\frac{4}{3}d$, etc.  For large $q$, the
number of codes we can consider becomes increasingly limited.

\begin{theorem}[Plotkin]
Let $C$ be an $(n,M,d)$ code over $\mathbb{F}_q$ such that $rn < d$ where $r = 1 - q^{-1}$.  Then
\begin{equation}
A_q(n,d) \le \left \lfloor \frac{d}{d-rn}\right\rfloor
\end{equation}
\end{theorem}

\begin{proof}
Let 
\begin{equation} \label{plotkin_1}
S = \sum_{x \in \mathcal{C}} \sum_{y \in \mathcal{C}} \text{d}(x,y)
\end{equation}

Note that for $x,y \in \mathcal{C}$, d$(x,y)=0$ for $x=y$, and $d \le$ d$(x,y)$ for $x\neq y$.  This implies that
\begin{equation}
M(M-1)d\le S
\end{equation}

This comes directly from equation \ref{plotkin_1}.  We have $M$ possible codewords to consider for $x$ in the outer summation, $M-1$ distinct codewords from $x$ to consider in the inner summation for $y$, and the distance between $x$ and $y$ will always be greater than or equal to $d$.

Next, let $\mathcal{M}$ be the $M \times n$ matrix whose rows are the codewords of $\mathcal{C}$.  For $1 \le i \le n$, let $n_{i,\alpha}$ be the number of times $\alpha \in
 \mathbb{F}_q$ occurs in column $i$ of $\mathcal{M}$.  Note that $\sum_{\alpha \in \mathbb{F}_q} n_{i,\alpha} = M$ for $1\le i \le n$.  This is simply because there are $M$ total
 elements of $\mathbb{F}_q$ in each column, so the sum over all $n_{i,\alpha}$ must necessarily be $M$.  Consequently, we have

\begin{equation}
\begin{split}
S = \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}(M - n_{i,\alpha}) &= M\sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha} - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \\
&= nM^2 - \sum_{i=1}^{n} \sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2
\end{split}
\end{equation}

Recall the Cauchy-Schwarz inequality, which states that 
\begin{equation}
\left(\sum_{i=1}^n x_i y_i \right )^2 \le \left(\sum_{i=1}^n x_i^2 \right ) \left(\sum_{i=1}^n y_i^2 \right )
\end{equation}

For our purposes, this means that 
\begin{equation}
\left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 \le q \left(\sum_{\alpha\in\mathbb{F}_q} n_{i,\alpha}^2 \right )
\end{equation}

Using this inequality, we obtain

\begin{equation}
S \le nM^2 - \sum_{i=1}^n q^{-1} \left(\sum_{\alpha\in\mathbb{F}_q} 1\cdot n_{i,\alpha} \right )^2 = nM^2 - \frac{nM^2}{q} = nrM^2
\end{equation}

Combining the two, we get FINISH.

\end{proof}

@@

@@
